SMT-Boosted Security Types for Low-Level MPC

### 2024-10-14 esop25/frontmatter.tex
add a bit in introduction
checkpoint

\newcommand{\theabstract}{
  \begin{abstract}
  Secure Multi-Party Computation (MPC) is an important enabling
  technology for data privacy in modern distributed applications. We
  devevelop a new type theory to automatically enforce correctness,
  confidentiality, and integrity properties of protocols written in
  the \emph{Prelude/Overture} language framework. Judgements in the
  type theory are predicated on SMT verifications in a theory of
  finite fields, which supports precise and efficient analysis. Our
  approach is compositional, scalable, and generalizes to arbitrary
  prime fields for data and key sizes.
\end{abstract} }

>>>>

\newcommand{\theabstract}{
  \begin{abstract}
  Secure Multi-Party Computation (MPC) is an important enabling
  technology for data privacy in modern distributed applications. We
  develop a new type theory to automatically enforce correctness,
  confidentiality, and integrity properties of protocols written in
  the \emph{Prelude/Overture} language framework. Judgements in the
  type theory are predicated on SMT verifications in a theory of
  finite fields, which supports precise and efficient analysis. Our
  approach is automated, compositional, scalable, and generalizes to arbitrary
  prime fields for data and key sizes.
\end{abstract} }
